Estimating the size of a population through repeated sampling: a new view on capture-recapture procedures

### 2022-03-08 _900_output/paper/paper.tex
Some further changes to paper body

\author{G. KAUERMANN, N. SAPARGALI}
\affil{Department of Statistics, Ludwig-Maximilians-Universität München, 80539 Munich, Germany
\email{nurzhan.sapargali@stat.uni-muenchen.de} \email{goeran.kauermann@stat.uni-muenchen.de}}

@@

\section{Model}
Consider a closed population of $N$ individuals $(i = 1,\ldots, N)$ from which we draw $T$ samples $(t = 1,\ldots, T)$ using some sampling scheme. Define $S_t$ to be the set of individuals included into sample $t$ and $n_t$ to be the size of $S_t$. Furthermore, let $\pi_i$ and $X_{i(T)}$ denote respectively the inclusion probability of $i$ and the count of $i$ being included into a sample after $T$ draws
\begin{equation*}
\pi_i = \text{pr}(i \in S_t), \quad X_{i(T)} = \sum_{t=1}^T \mathds{1}\{i \in S_t\};
\end{equation*}
If $n_t = n$ for all $t$ and $\pi_i = n / N$ for all $i$, then $X_{i(T)}$ iid

\end{document}

>>>>

\author{G. KAUERMANN, N. SAPARGALI}
\affil{Department of Statistics, Ludwig-Maximilians-Universität München, 80539 Munich, Germany
\email{goeran.kauermann@stat.uni-muenchen.de} \email{nurzhan.sapargali@stat.uni-muenchen.de}}

@@

\section{Model and likelihood}
Our starting point is a basic capture-recapture model with equal capture probabilities. Consider a closed population $\mathcal{P} = \{1,\ldots,N\}$ from which we draw $T > 1$ independent samples of size $n$ using some sampling scheme. Define $S_t$ to be the set of individuals included into sample $t$ and $\pi_i = \text{pr}(i \in S_t)$ to be the inclusion probability of $i$. Let $X_{i(T)}$ denote the frequency count of $i$ being included into $T$ samples
\begin{equation*}
X_{i(T)} = \sum_{t=1}^T \mathds{1}\{i \in S_t\};
\end{equation*}
If $\pi_i = n / N$ for all $i$, then $X_{1(T)}, \ldots, X_{N(T)}$ are modeled as identically and independently distributed binomial variables
\begin{equation*}
\text{pr}(X_{i(T)} = x_i) = \binom{T}{x_i} \left(\frac{n}{N}\right)^{x_i} \left(1 - \frac{n}{N}\right)^{T - x_i}
\end{equation*}
However, since we only observe $X_{i(T)} > 0$, the above distribution must be truncated at zero. For convenience purposes, it is useful to decompose $\mathcal{P}$ into $S^{in}_T = \{i \in \mathcal{P}: X_{i(T)} > 0\}$ and $S^{out}_T = \{i \in \mathcal{P}: X_{i(T)} = 0\}$. The likelihood function is then
\end{document}
